---
title: "Lab 8"
author: "Nur Izzati Binti Shalahudin"
date: '2022-05-13'
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE,message = FALSE}
library(mlbench)
library(caret)
library(Hmisc)
library(dplyr)
```

### Get dataset & clean it
```{r,warning=FALSE}
data("BreastCancer")
breast <- BreastCancer

#remove 1st column (ID column, not needed)
breast <- select(breast, -1)

#impute NA values in bare.nuclei into mean value
breast$Bare.nuclei<-as.numeric(breast$Bare.nuclei)
breast$Bare.nuclei[is.na(breast$Bare.nuclei)] <-round(mean(breast$Bare.nuclei, na.rm = T),digits = 0)

#change 'Class' into factors
breast$Class<-as.character(breast$Class)
breast$Class<-as.factor(breast$Class)

# set seed
set.seed(7)

# traincontrol
trainControl <- trainControl(method="repeatedcv", number=10, repeats=3)
metric <- "Accuracy"
```


# **Linear Algorithm**

### Linear Regression (LR)
```{r,warning=FALSE}
fit.glm= train(Class~.,
                data=breast, 
                method="glm",
                metric=metric,
                trControl=trainControl)
```

### Linear Discriminate Analysis (LDA)
```{r}
lda.fit = train(Class ~ ., data=breast, method="lda",metric=metric,
                trControl=trainControl)
```

### Regularized Logistic Regression (GLMNET)
```{r}
glmnet.fit<-train(Class ~ ., data=breast, method="glmnet",metric=metric,
           trControl=trainControl)
```









# **Non-Linear Algorithm**

### k-Nearest Neighbors (kNN)
```{r}
knn.fit<-train(Class ~ ., data=breast, method="knn",metric=metric,
                  trControl=trainControl)

```

### Classification and Regression Trees (CART)
```{r}
cart.fit<-train(Class ~ ., data=breast, method="rpart",metric=metric,
               trControl=trainControl)

```

### Naive Bayes (NB)
```{r}
nb.fit<-train(Class ~ ., data=breast, method="naive_bayes",metric=metric,
                trControl=trainControl)

```

# **Result**
```{r}
print(fit.glm)
print(lda.fit)
print(glmnet.fit)
print(knn.fit)
print(cart.fit)
print(nb.fit)
```








# **Ways to improve performance of model**
### 1.Add more data for malignant cases (bcs benign cases have 2x more data)
### 2.Ensure the data collected are complete (no NA/NAN)

